An Efficient Interpolation Technique for Jump Proposals in Reversible-Jump Markov Chain Monte Carlo Calculations

### 2010-12-08 paper.tex
.

\section{Examples}

\section{Other Uses}

\section{Conclusion}

>>>>

\section{Example}

BH mass paper [still not sure how to present this without repetition...  ]

\section{Conclusion/Discussion}

...

\subsection{Other Uses}
The efficient interpolation of a PDF via a kD-tree described in this paper can be extremely useful in other contexts, beyond a reversible-jump MCMC.  We suggest two examples below: generating efficient jump proposal distributions and convergence tests?

...

Mention nested sampling?
